---
title: "My Very Fun Markdown"
author: "Kiran Hegde @ ODSC"
date: "May 2, 2018"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
    pdf_document:
        toc: yes
        number_sections: truex
---
# Global settings
Below will set a global settings to cache = TRUE

```{r settings, include=FALSE, }
knitr::opts_chunk$set(cache = TRUE)
```


#My First section

We started a new section with a hashtag and this is the first paragraph in that section. Spacing is important, so be aware of that. Adding a third sentence so that I have a full paragraph to meet antiquated rules of grammar which might not apply any more. And I'll start a sentence with and. J.D. Salinger rules!!!!!

Leaving a blank line before the next text starts a new paragraph.

# New Section

You start a new section simple by creating a new one with a hashtag. There is no need to close the old section.

# Subsections

Creating subsections is just as easy, we simply use two hastags.

## First Subsection

We started a Subsection, with a section with 2 hashtags and didn't need to do anything to the outer section.

## Another subsection

Another subsection is just like making the first subsection, just use two hashtags. Again, no need to close the prior subsection

#Back to section

Repeating the point, you start a new section, even after subsections, simply by creating a new one with a single hashtag. No closing anything.

#Formatting Text

_Emphasized Text_

__Strong Text__

___Emphasized and Bold Text___

`anything in backticks looks like computer code, or typewrite text`

# Lists

## Unordered Lists

 - Apple
 - Banana
 - Orange
 - Kiwi
 - Durian
 - Watermelon
 
## Ordered Lists

1. New York
1. New Jersey
1. Detriot
1. Naples
1. Rome

a. Beer
a. Guiness
a. Blue Moon
a. Oberon

1. New York
1. New Jersy
1. New Haven
1. Detroit

## Nested Lists

1. New York
    1. Coal
    1. Woood
    1. Gas
1. New Jersey
    - Gas
    - Wood
1. Naples

# link

[My website](http://www.hegdekiran.com)

# R Time!!!!!!!!
# Alt + Ctrl + i

```{r}
1+1

```

```{r}
x <-3
x
```

```{r}
x*2
```

Let's give our chunks names.
```{r simple-code-ex}
x*3 + 7
```
Let's show the results of a chunk without seeing the code.

```{r another-example,echo=FALSE}
5*x + 4
```

# Plots

```{r load-ggplot2}
library(ggplot2)
```


```{r plot-diamonds, fig.align='center', fig.cap='A Scatter plot of diamond price vs size , color coded according to diamond cut.', cache=TRUE }

ggplot(diamonds, aes(x=carat, y=price, color=cut)) +
    geom_point()
```


